MCLM parameters, interactive example

### 2024-05-14 apps/Graphical_representation_interactive.qmd
Adds spike drawing logic (for single latent trait)
Adds input disabling logic (WiP)

useShinyjs()

@@

    # Compute coordinates in transformed (i.e. orthonormal) space:
    lt_sample() |>
      rowid_to_column() |>
      pivot_longer(-rowid) |>
      group_by(rowid) |>
      mutate(value = transf_matrix %*% value |> drop()) |>
      pivot_wider()
  })
)
```

@@

>>>>

@@

    # Compute coordinates in transformed (i.e. orthonormal) space:
    lt_sample() |>
      rowid_to_column() |>
      pivot_longer(-rowid) |>
      group_by(rowid) |>
      mutate(value = transf_matrix %*% value |> drop()) |>
      pivot_wider()
  })
)

## FIXME: Disabling inputs does not work
# useShinyjs()
# observeEvent(
#   input$sample_type == "unique value",
#   disable('N')
# )
# observeEvent(
#   input$sample_type == "sample",
#   {
#     disable('theta_1')
#     disable('theta_2')
#   }
# )
```

@@

draw_spikes <- reactiveVal() # Flag to indicate whether to draw spikes (for
                             #   single value plotting only)
observeEvent( ## TODO: Draw spikes
  input$sample_type,
  draw_spikes(input$sample_type == "unique value")
)
